### 2023-03-09 REV_Polak1/Polak1.tex
Additional corrections added

\begin{newrevengenv}{Paweł Polak}
	{Why is neuron modeling of particular philosophical interest?}
	{Why is neuron modeling of particular philosophical interest?}
	{Why is neuron modeling of particular philosophical interest?}
	{Pontifical University of John Paul II in Kraków}
	{Andrzej Bielecki, \textit{Models of Neurons and Perceptrons: Selected Problems and Challenges}, Studies in Computational Intelligence, vol. 770, Springer International Publishing, Cham 2019, pp. 156.}
%	; Studies in Computational Intelligence Volume vol. 770, DOI: \href{https://doi.org/10.1007/978-3-319-90140-4}{10.1007/978-3-319-90140-4}.}

@@

\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{A}{}peculiarity of ``philosophy in science''
%\label{ref:RNDSoIfWpdNhG}(see Heller, 2019; Polak, 2019)
\parencites[see][]{heller_how_2019}[][]{polak_philosophy_2019} %
 is that the best sources tend to be atypical from the viewpoint of most philosophers: For example, on the one hand, there are works that popularize science, while on the other hand, there are research articles and even specialized monographs. The book discussed here falls into the last category, and it is devoted to modeling neurons and perceptrons. It was written by a~mathematician from Kraków, Andrzej Bielecki, who is currently working at the AGH University of Science and Technology.\footnote{Andrzej Bielecki received an M.Sc. degree in Physics and Mathematics and a~Ph.D. in Mathematics, D.Sc. (habilitation) in Mathematics from the Jagiellonian University in Kraków. He obtained a~professorship in Computer Science in 2020. His fields of interest includes dynamical systems theory, artificial intelligence, cybernetics, and philosophy of science, and he has written over 120 scientific papers and one textbook.} Readers of \textit{ZFN}, as well as the related \textit{Semina Scientiarum} journal, will probably associate him with the philosophical activities that he has practiced within the context of his scientific activities 
%\label{ref:RNDkz8F1S0BJI}(Bielecki, 2016; 2018).
\parencites*[][]{bielecki_cybernetyczna_2016}[][]{bielecki_epistemologiczne_2018}. %
 Bielecki is an example of a~scientist–philosopher from the Krakow milieu,\footnote{It is worth mentioning that in the book, Bielecki mostly uses examples from research conducted in the Kraków milieu. The use of the cybernetic theory framework could also be interpreted as another sign of the local milieu's influence.} and it is worth noting that he develops his philosophical activities, among other things, through his work on the Committee on Philosophy of Science at the Polish Academy of Arts and Sciences in Kraków.

>>>>

\begin{newrevengenv}{Paweł Polak}
	{Why is neuron modeling of particular philosophical interest?}
	{Why is neuron modeling of particular philosophical interest?}
	{Why is neuron modeling of particular philosophical interest?}
	{Pontifical University of John Paul II in Kraków, Poland}
	{Andrzej Bielecki, \textit{Models of Neurons and Perceptrons: Selected Problems and Challenges}, Studies in Computational Intelligence, vol. 770, Springer International Publishing, Cham 2019, pp. 156.}
%	; Studies in Computational Intelligence Volume vol. 770, DOI: \href{https://doi.org/10.1007/978-3-319-90140-4}{10.1007/978-3-319-90140-4}.}

@@

\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{A}{}peculiarity of ``philosophy in science''
%\label{ref:RNDSoIfWpdNhG}(see Heller, 2019; Polak, 2019)
\parencites[see][]{heller_how_2019}[][]{polak_philosophy_2019} %
 is that the best sources tend to be atypical from the viewpoint of most philosophers: For example, on the one hand, there are works that popularize science, while on the other hand, there are research articles and even specialized monographs. The book discussed here falls into the last category, and it is devoted to modeling neurons and perceptrons. It was written by a~mathematician from Kraków, Andrzej Bielecki, who is currently working at the AGH University of Science and Technology.\footnote{Andrzej Bielecki received an M.Sc. degree in Physics and Mathematics and a~Ph.D. in Mathematics, D.Sc. (habilitation) in Mathematics from the Jagiellonian University in Kraków. He obtained a~professorship in Computer Science in 2020. His fields of interest includes dynamical systems theory, artificial intelligence, cybernetics, and philosophy of science, and he has written over 120 scientific papers and one textbook.} Readers of \textit{Philosophical Problems in Science/Zagadnienia Filozoficzne w Nauce} (ZFN), as well as the related \textit{Semina Scientiarum} journal, will probably associate him with the philosophical activities that he has practiced within the context of his scientific activities 
%\label{ref:RNDkz8F1S0BJI}(Bielecki, 2016; 2018).
\parencites*[][]{bielecki_cybernetyczna_2016}[][]{bielecki_epistemologiczne_2018}. %
 Bielecki is an example of a~scientist–philosopher from the Krakow milieu,\footnote{It is worth mentioning that in the book, Bielecki mostly uses examples from research conducted in the Kraków milieu. The use of the cybernetic theory framework could also be interpreted as another sign of the local milieu's influence.} and it is worth noting that he develops his philosophical activities, among other things, through his work on the Committee on Philosophy of Science at the Polish Academy of Arts and Sciences in Kraków.

### 2023-03-09 REV_Polak2/Polak2.tex
Additional corrections added

\begin{newrevengenv}{Paweł Polak}
	{Beyond epistemic concepts of information: The case of ontological information as philosophy in science}
	{Beyond epistemic concepts of information\ldots}
	{Beyond epistemic concepts of information: The case of ontological\\information as philosophy in science}
	{Pontifical University of John Paul II in Kraków}
	{Roman Krzanowski, \textit{Ontological information: information in the physical world, series: World Scientific series in information studies}, 13, Hackensack, NJ: World Scientific 2022, pp. xii+264.}

@@

However, while most of the published works on information see information through Shannon's lenses the focus of Roman Krzanowski's book
%\label{ref:RNDj1wWmH95Df}(Krzanowski, 2022)
\parencite[][]{krzanowski_ontological_2022} %
 is physical information. i.e., information that is not associated with knowledge or communication (Shannon's legacy), and that it is a~part of nature as other physical phenomena are; the conceptualization of information has not been widely accepted by the scientific community.

The first significant step was to distinguish between concepts of epistemic information (as found in Shannon's theory) from theories about ontological information. The author's second step was rather than constructing a~concept of information \textit{a~priori}, to proceed in the spirit of the Kraków school of philosophy in science
%\label{ref:RND6l6ZUmsrmK}(Heller, 2019; Polak, 2019; Polak and Trombik, 2022).
\parencites[][]{heller_how_2019}[][]{polak_philosophy_2019}[][]{polak_krakow_2022}. %
 Krzanowski searches for the meaning of ontological information g~attributed to it by reserachers and tries to understand the philosophical basis for using such concept. This is no coincidence, because in the pages of the associated journal ``Philosophical Problems in Science/Zagadnienia Filozoficzne w~Nauce'' (ZFN), the problem of information in science has been discussed from the very beginning to the current day 
%\label{ref:RNDqB1suQWgaa}(Turek, 1978; 1981; Krzanowski, 2017; 2020).
\parencites*[][]{turek_filozoficzne_1978}[][]{turek_rozwazania_1981}[][]{krzanowski_minimal_2017}[][]{krzanowski_why_2020}.%

@@

\begin{itemize}
\item (C1) Information is quanti[FB01?]able.
\item (C2) Changes in the organization of physical objects can be denoted as a~form of computation or information processing.
\end{itemize}
After the critical discussion, Krzanowski posits that these three properties and two corollaries are indispensable for the definition and understanding of the concept of ontological information.. This set of properties has a~hypothetical status, and this conceptualization is relative to actual science, so it is open to future changes together with the entirety of scientific knowledge.

@@

\vspace{15mm}%
{\subsubsectit{\hfill Abstract}}\\
{[to be inserted afterr the proofreading]

[to set pages range in rereference (Mścisławski, 2022) during typesetting ?]}\par%
\vspace{2mm}%
{\subsubsectit{\hfill Keywords}}\\
{ontological information, Mark Burgin}%

>>>>

\begin{newrevengenv}{Paweł Polak}
	{Beyond epistemic concepts of information: The case of ontological information as philosophy in science}
	{Beyond epistemic concepts of information\ldots}
	{Beyond epistemic concepts of information: The case of ontological\\information as philosophy in science}
	{Pontifical University of John Paul II in Kraków, Poland}
	{Roman Krzanowski, \textit{Ontological information: information in the physical world, series: World Scientific series in information studies}, 13, Hackensack, NJ: World Scientific 2022, pp. xii+264.}

@@

However, while most of the published works on information see information through Shannon's lenses the focus of Roman Krzanowski's book
%\label{ref:RNDj1wWmH95Df}(Krzanowski, 2022)
\parencite[][]{krzanowski_ontological_2022} %
 is physical information i.e., information that is not associated with knowledge or communication (Shannon's legacy), and that it is a~part of nature as other physical phenomena are; the conceptualization of information has not been widely accepted by the scientific community.

The first significant step was to distinguish between concepts of epistemic information (as found in Shannon's theory) from theories about ontological information. The author's second step was rather than constructing a~concept of information \textit{a~priori}, to proceed in the spirit of the Kraków school of philosophy in science
%\label{ref:RND6l6ZUmsrmK}(Heller, 2019; Polak, 2019; Polak and Trombik, 2022).
\parencites[][]{heller_how_2019}[][]{polak_philosophy_2019}[][]{polak_krakow_2022}. %
 Krzanowski searches for the meaning of ontological information g~attributed to it by reserachers and tries to understand the philosophical basis for using such concept. This is no coincidence, because in the pages of the associated journal ``Philosophical Problems in Science/Zagadnienia Filozoficzne w~Nauce'' (ZFN), the problem of information in science has been discussed from the very beginning to the current day 
%\label{ref:RNDqB1suQWgaa}(Turek, 1978; 1981; Krzanowski, 2017; 2020).
\parencites[][]{turek_filozoficzne_1978}[][]{turek_rozwazania_1981}[][]{krzanowski_minimal_2017}[][]{krzanowski_why_2020}.%

@@

\begin{itemize}
\item (C1) Information is quantifiable.
\item (C2) Changes in the organization of physical objects can be denoted as a~form of computation or information processing.
\end{itemize}
After the critical discussion, Krzanowski posits that these three properties and two corollaries are indispensable for the definition and understanding of the concept of ontological information. This set of properties has a~hypothetical status, and this conceptualization is relative to actual science, so it is open to future changes together with the entirety of scientific knowledge.

@@

\vspace{15mm}%
{\subsubsectit{\hfill Abstract}}\\
{This review article discusses the book of Roman Krzanowski, \textit{Ontological Information: Information in the Physical World}, which is published by World Scientific. Krzanowski’s book makes a very important contribution to the contemporary discussion about the nature of information. The author analyzes the concept of ontological information and its uses in the works of scientists from various disciplines, resulting in an innovative and inspiring analysis that every philosopher involved in the philosophy of information should read.}\par%
\vspace{2mm}%
{\subsubsectit{\hfill Keywords}}\\
{ontological information, philosophy in science, Mark Burgin}%
